A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Add first draft conclusion.

\begin{align}
\text{\em 2-precision} &= \left|\left\{(u,v) \in P | d_L(u,v) \leq 2
\right\}\right|
\\\text{\em 2-recall} &= \left|\left\{(u,v) \in L | d_P(u,v) \leq 2
\right\}\right|
\\\text{\em 2-}F_1 &= 2\cdot \frac{\text{\em 2-precision} \cdot \text{\em
2-recall}}{\text{\em 2-precision} + \text{\em 2-recall}}
\end{align}
where $P$ is the set of predicted edges, $L$ is the set of lost edges (i.e.
those in the cut resulting from the partition), $d_L(u,v)$ is the shortest
distance between nodes $u$ and $v$ in the original unpartitioned graph, and
$d_P(u,v)$ is the shortest distance between nodes $u$ and $v$ in the new graph
formed using the predicted edges in $P$.

@@

Figures 1 and 2 show the top and bottom most relevant items for two of the sixteen
concepts learned for the Women's Dresses category. Note that concepts learned by
SVD range from positive to negative, representing the two extremes of the
concept.

\begin{figure}
\centering
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos1.jpg}
\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos2.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos3.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos4.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_pos5.jpg}
\label{fig:sub2}
\end{subfigure}
\subcaption{The top 5 items, representing the positive direction}

\centering
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg1.jpg}
\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg2.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg3.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg4.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept1_neg5.jpg}
\label{fig:sub2}
\end{subfigure}
\subcaption{The bottom 5 items, representing the negative direction}
\label{fig:conceptA}
\title{Figure 1: The top and bottom items representing a concept in the Dresses
category.  This concept could be characterized as modern and tiered in the
positive direction, and gown-like and elegant in the negative direction.}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos1.jpg}
\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos2.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos3.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos4.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_pos5.jpg}
\end{subfigure}
\subcaption{The top 5 items, representing the positive direction}

\centering
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg1.jpg}
\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg2.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg3.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg4.jpg}
\label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.18\textwidth}
\centering
\includegraphics[width=\linewidth]{concepts/concept2_neg5.jpg}
\label{fig:sub2}
\end{subfigure}
\subcaption{The bottom 5 items, representing the negative direction}
\title{Figure 2: The top and bottom items representing another different Dresses
concept. This concept could be characterized as two-toned and playful in the
positive direction, and belted and light in the negative direction.}
\label{fig:conceptB} \end{figure}

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.0\textwidth]{PopularityHistogram.png}
	\caption{The top 25 most popular items and how many times they appear in
    recommendations. Here we compare the distribution of gold-standard
    recommendations (red) to the recommendations predicted by the
    $LatentFeatureRecommender$ with (blue) and without (yellow) popularity. The
    yellow bars are small and barely visible. This plot was generated on the
    Women's Dresses category.}
    \label{fig:PopularityHistogram}
\end{figure}

@@

\section*{Conclusion}
We tried a few different methods for creating recommendations between
retailers. We find that this one is the best.
The last method uses an unconventional approach that adds some value in the
process. These results could be used in real life for these problems, since all
of the data exists.

\section*{Future Work}
Incorporate more data such as customer reviews. Use computer vision techniques.
Focus more on popular hubs model.

>>>>

\begin{align}
\text{\em 2-precision} &= \left|\left\{(u,v) \in P | d_L(u,v) \leq 2
\right\}\right|
\\\text{\em 2-recall} &= \left|\left\{(u,v) \in L | d_P(u,v) \leq 2
\right\}\right|
\\\text{\em 2-}F_1 &= 2\cdot \frac{\text{\em 2-precision} \cdot \text{\em
2-recall}}{\text{\em 2-precision} + \text{\em 2-recall}},
\end{align}
where $P$ is the set of predicted edges, $L$ is the set of lost edges (i.e.
those in the cut resulting from the partition), $d_L(u,v)$ is the shortest
distance between nodes $u$ and $v$ in the original unpartitioned graph, and
$d_P(u,v)$ is the shortest distance between nodes $u$ and $v$ in the new graph
formed using the predicted edges in $P$.

@@

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.0\textwidth]{PopularityHistogram.png}
	\caption{The top 25 most popular items and how many times they appear in
    recommendations. Here we compare the distribution of gold-standard
    recommendations (red) to the recommendations predicted by the
    $LatentFeatureRecommender$ with (blue) and without (yellow) popularity. The
    yellow bars are small and barely visible.}
    \label{fig:PopularityHistogram}
\end{figure}

@@

\section*{Conclusion}
In this study, we address the problem of determining inter-retailer, or
inter-catalogue, item-item associations. We frame this problem as a recommender
problem, which motivates a relatively straightforward experiment in which a
candidate algorithm must connect two recommendation graphs by guessing edges
between them.

In this work, we introduced a novel technique for predicting item-item
associations across retailers. This technique employs {\em Topic-Sensitive
PageRank} on a publicly available recommendation graph to generate simulated
user data. With this data, we perform {\em Latent Semantec Indexing} to learn a
latent feature space for items from in a particular online catalogue. By
generalizing the notion of {\em Term Frequency---Inverse Document Frequency}
score, we construct proxy tf-idf vectors for the latent dimensions, or {\em
concepts}, associated with a particular catalogue. This, in turn, allows us to
construct a transformation matrix such that vectors in one catalogue's concept
space can be transformed into another catalogue's concept space. Inter-catalogue
associations can then be made by finding pairs of items that are a minimal
distance apart in a common concept space.

This technique is improved upon by incorporating the notion of item {\em
popularity} $\rho$, which we define in this context to be the logarithm of the
item's degree within its associated recommendation graph. We show that $\rho$
can be used in multiple ways to improve the performance of an inter-retailer
recommender system.

Finally, we compared our latent inter-catalogue recommender system to several
nontrival baseline algorithms and find that it outperforms all of them in both
standard precision and recall of gold-standard inter-catalogue edges as well as
another combination of informative metrics we call {\em 2-precision} and {\em
2-recall}.

Making accurate item-item associations across retailers using only publicly
available information is a challenging problem. The ability to accurately
identity these relationships, however, could potentially provide a retailer or
other service provider with valuable business intelligence.
